H~3~: Issue area

### 2023-08-29 notebook/results-crackdown.qmd
Move labeling functions to targets
Better hypothesis icons

# Helpful functions
label_pp <- label_number(accuracy = 1, scale = 100, 
  suffix = " pp.", style_negative = "minus")

fmt_decimal <- label_number(accuracy = 0.001, style_negative = "minus")

@@

::: {.callout-tip}
## H~2a~: Relationship with host government

@@

::: {.callout-tip}
## H~2b~: Organization and relationship with host government

>>>>

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 2~a~: Relationship with host government

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 2~b~: Organization and relationship with host government

### 2023-08-29 notebook/results-issue.qmd
Move labeling functions to targets
Better hypothesis icons

::: {.callout-tip}
## H~3a~: Issue area

@@

::: {.callout-tip}
## H~3b~: Relationship with host government and issue area

>>>>

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 3~a~: Issue area

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 3~b~: Relationship with host government and issue area
